---
title: "SQL_to_R"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Read SQL Database into R

## Intall or load required packages
```{r}
library(DBI)
library(RSQLite)
```

## Establish database connection
```{r}

mydb <- dbConnect(RSQLite::SQLite(),"../Data/mlks_parsed.db")
```

## Laod Project data from database
```{r}
df <- dbGetQuery(mydb, 'SELECT * from Projects')
```

## Drop data that will not be analyzed
```{r}
#Get a list of all columns
names(df)

#Drop ID fields
drop_ids <- c("project_id", "profile_id", "profile_project_id")
df <- df[ , !(names(df) %in% drop_ids)]
```


## Examine result distribution of projects
```{r}
df %>%
  ggplot() +
  aes(df$state) +
  geom_histogram(stat ="count")
```

##Determine Outcome Variable Methodology
After examining the discrepencies between state: "successful" and goal_met, we select $state to produce our outcome variable.
```{r}
#Isolate relevant variables into df_success
df_success <- df[,c("pledged", "usd_pledged", "state", "goal")]
df_success$pledged <- as.numeric(df_success$pledged)
df_success$usd_pledged <- as.numeric(df_success$usd_pledged)
df_success$goal <- as.numeric(df_success$goal)

#How does $pledged compare to $usd_pledged?
(mean(df_success$pledged == df_success$usd_pledged))

#Add $goal_met
df_success$goal_met <- df_success$usd_pledged >= df_success$goal

#Compare $state to $goal_met
df_success$successful <- df_success$state == "successful"
(mean(df_success$goal_met == df_success$successful))

#Explore the errors
df_errors <- df_success[df_success$goal_met != df_success$successful,]
df_errors

#Add outcome variables
df$successful <- as.numeric(df$state == "successful")

#Remove pseudo outcome variables
drop <- c("pledged", "usd_pledged")
df <- df[ , !(names(df) %in% drop)]

#Clean Up
rm(df_success)
rm(df_errors)

```
## Explore $backers_count
Backers count is a very strong predictor of success. We can see from the the logistic model that after ~75 backers succcess is almost guranteed. However, we are focusing on variables at the begining of a project.
```{r}
#Check for NA
anyNA(df$backers_count)

#Change to Numeric
df$backers_count <- as.numeric(df$backers_count)

#Linear Model
lm_backers_count <- glm(successful ~ backers_count, data = df)
summary(lm_backers_count)

#Logit; Filtered for visual 
df_backers_count_filtered <- df %>%
  filter(backers_count < 100)

logit_backers_count <- glm(successful ~ backers_count, data = df_backers_count_filtered, family=binomial(link='logit'))

df_backers_count_filtered %>%
  ggplot() +
  theme_minimal() +
  ggtitle("$backers_count Logistic Model") +
  geom_point(aes(x=backers_count, y=successful), colour = "black") +
  geom_point(aes(x=backers_count, y=logit_backers_count$fitted.values), colour = "red")

#Clean Up
rm(lm_backers_count)
rm(df_backers_count_filtered)
rm(logit_backers_count)

drop <- c("backers_count")
df <- df[ , !(names(df) %in% drop)]

=======
setwd("~/Documents/Academic/UIUC MBA/Spring 2018/Independent Study/")

mydb <- dbConnect(RSQLite::SQLite(),"mlks_parsed.db")
# using RSQLite and DBI
```

## Explore $disable_communication
This is not a user initiated setting, rather an effect of a project being suspended.
```{r}

df_filtered_disable_communicaiotn <- df %>%
  filter(disable_communication == "True")

df_filtered_state_suspended <- df %>%
  filter(state == "suspended")

rownames(df_filtered_disable_communicaiotn) == rownames(df_filtered_state_suspended)

#Drop suspension related columns
drop <- c("disable_communication", "suspended_at")
df <- df[ , !(names(df) %in% drop)]

#Clean Up
rm(df_filtered_disable_communicaiotn)
rm(df_filtered_state_suspended)
```

##Explore currency
Current data shows only US currency, and therefore these variables are not predictive. As data set grows, we may see the introduction of new currency.
```{r}
unique(df$currency)
unique(df$current_currency)
unique(df$currency_trailing_code)
unique(df$creator_chosen_currency)
unique(df$currency_symbol)

#Drop suspension related columns
drop <- c("currency", "current_currency", "currency_trailing_code", "creator_chosen_currency", "currency_symbol")
df <- df[ , !(names(df) %in% drop)]
=======
db <- dbGetQuery(mydb, 'SELECT * from Projects')
```




## Disconnect and Delete
To avoid potential issues from having multiple open connections
```{r}
dbDisconnect(mydb)
unlink("~/mlks_parsed.db")
```

## Make a Function to Handle Multiple db Files
Not sure if this will run, but a potential solution to merge multiple databases from scraping
```{r}
x <- "~/Documents/Academic/UIUC MBA/Spring 2018/Independent Study/"

SQL_to_R <- function(x) {
  db <- data.frame()
  setwd(x)
  files <- as.matrix(list.files(x))
  for (i in files) {
    mydb <- dbConnect(RSQLite::SQLite(), "i")
    db <- rbind(dbGetQuery(mydb, 'SELECT * from Projects'))
    dbDisconnect(mydb)
    unlink("~/i")
  }
}
```