---
title: "R Text Analysis"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up and Import Data
```{r}
library(dplyr)
#install.packages("tidytext")
library(tidytext)
library(anytime)
library(ggplot2)
library(car)
library(lubridate)
#install.packages("DBI")
library(DBI)
#install.packages("RSQLite")
library(RSQLite)

setwd("~/Documents/Academic/UIUC MBA/Spring 2018/Independent Study/")
mydb <- dbConnect(RSQLite::SQLite(),"mlks_parsed.db")
db <- dbGetQuery(mydb, 'SELECT * from Projects')
dbDisconnect(mydb)
unlink("~/mlks_parsed.db")
```

## Clean Data
```{r}
# If statement to check redundant variables
i <- 1
if(db$profile_id[i] == db$profile_project_id[i]) {
  i = i + 1
  } else {
    print("FALSE")
    i - i + 1
  }
i <- 1
if(db$blurb[i] == db$profile_blurb[i]) {
  i = i + 1
  } else {
    print("FALSE")
    i - i + 1
  }
i <- 1
if(db$currency[i] == db$current_currency[i]) {
  i = i + 1
  } else {
    print("FALSE")
    i - i + 1
  }
i <- 1
if(db$pledged[i] == db$usd_pledged[i]) {
  i = i + 1
  } else {
    print("FALSE")
    i - i + 1
  }

# Check variables with only one level
VariableProfile <- c()
for (m in names(db)) {
  VariableProfile <- c(colnames(db), length(unique(db[[m]])))
}

unique(db$currency_trailing_code)
unique(db$creator_is_registered)
unique(db$livestreams)
unique(db$static_usd_rate)
unique(db$fx_rate)
unique(db$items)
unique(db$usd_type)
unique(db$currency_symbol)
unique(db$country)

# Format variables
# Date and time
db$deadline <- anytime(as.numeric(db$deadline))
db$profile_state_changed_at <- anytime(as.numeric(db$profile_state_changed_at))
db$state_changed_at <- anytime(as.numeric(db$state_changed_at))
db$successful_at <- anytime(as.numeric(db$successful_at))
db$updated_at <- anytime(as.numeric(db$updated_at))
db$launched_at <- anytime(as.numeric(db$launched_at))
db$created_at <- anytime(as.numeric(db$created_at))
db$failed_at <- anytime(as.numeric(db$failed_at))
db$canceled_at <- anytime(as.numeric(db$canceled_at))
db$potd_at <- anytime(as.numeric(db$potd_at))
db$suspended_at <- anytime(as.numeric(db$suspended_at))

# Remove unwanted or redundant variables
db_cleaned <- select(db, 
                     -profile_project_id, 
                     -static_usd_rate, 
                     -urls_api_project, 
                     -fx_rate, 
                     -urls_api_updates, 
                     -urls_api_comments, 
                     -currency_trailing_code, 
                     -urls_web_project, 
                     -profile_blurb, 
                     -items, 
                     -current_currency, 
                     -creator_is_registered, 
                     -livestreams, 
                     -photo_little, 
                     -category_urls_web_discover, 
                     -profile_feature_image_attributes_image_urls_default, 
                     -location_urls_web_discover, 
                     -location_urls_web_location, 
                     -usd_pledged, 
                     -usd_type, 
                     -photo_small, 
                     -photo_1024x576, 
                     -profile_feature_image_attributes_image_urls_baseball_card, 
                     -creator_avatar_thumb, 
                     -creator_urls_web_user, 
                     -photo_thumb, 
                     -currency_symbol, 
                     -photo_ed, 
                     -urls_web_updates, 
                     -country, 
                     -photo_med, 
                     -photo_full, 
                     -photo_1536x864, 
                     -creator_avatar_medium, 
                     -creator_avatar_small, 
                     -creator_urls_api_user, 
                     -photo_key)
db_cleaned <- mutate(db_cleaned, 
                     hype_length = round(((launched_at - created_at)/(24)), 2), # convert from min to hours
                     campaign_length = round((deadline - launched_at)*24, 2), # convert from days to hours
                     percent_funded = round((as.numeric(pledged)/as.numeric(goal)*100), 2), 
                     avg_contribution = round((as.numeric(pledged)/as.numeric(backers_count)), 2))
```

## Exploratory Analysis
Conclusions:
- Need outlier detection and exclusion for all outcome variables (percent_funded, backers_count, avg_contribution).
- Non-normal distribution of percent_funded.
- Goal amount doesn't seem important to percent_funded.
- Apparently normal distribution of avg_contribution, but skewed due to outliers.
- More projects were launched over time, but the 
- Some categories never fail in this dataset (only considered if n > 5):
  - design/product design (76 projects)
  - film & video/documentary (607 projects)
  - film & video/shorts (938 projects)
  - games/tabletop games (41 projects)
- Most successful high-level categories (only considered if n > 10):
  - Design 145 projects 82% successful
  - Film & Video 2,688 projects 75% successful
  - Music 3,128 projects 66% successful
```{r}
boxplot(db_cleaned$percent_funded)
boxplot(as.numeric(db_cleaned$backers_count))
boxplot(db_cleaned$avg_contribution)

db_cleaned %>% 
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  ggplot() + 
  geom_histogram(aes(x = percent_funded))

db_cleaned %>% 
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  ggplot() + 
  geom_point(aes(x = campaign_length, y = percent_funded))

db_cleaned %>% 
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  ggplot() + 
  geom_point(aes(x = hype_length, y = percent_funded))

db_cleaned %>% 
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  ggplot() + 
  geom_point(aes(x = goal, y = percent_funded))

db_cleaned %>% 
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  ggplot() + 
  geom_point(aes(x = category_parent_id, y = percent_funded))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_histogram(aes(x = avg_contribution))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_point(aes(x = id, y = avg_contribution))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_point(aes(x = campaign_length, y = avg_contribution))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_point(aes(x = hype_length, y = avg_contribution))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_point(aes(x = goal, y = avg_contribution))

db_cleaned %>% 
  filter(!is.na(avg_contribution) & avg_contribution <= 250) %>%
  ggplot() + 
  geom_point(aes(x = category_id, y = avg_contribution))

db_cleaned %>%
  filter(!is.na(launched_at)) %>%
  ggplot() +
  geom_histogram(aes(x = launched_at))

db_cleaned %>%
  filter(!is.na(percent_funded) & percent_funded <= 400) %>%
  group_by(month = floor_date(as.Date(launched_at), "month"))  %>% 
  summarise(n(), 
            mean(percent_funded, na.rm = TRUE), 
            mean (avg_contribution, na.rm = TRUE))

db_cleaned %>%
  filter(percent_funded <= 400 & avg_contribution <= 250) %>%
  group_by(state) %>%
  summarise(n(),
            mean(percent_funded, na.rm = TRUE), 
            mean(avg_contribution, na.rm = TRUE), 
            mean(goal, na.rm = TRUE),
            sd(percent_funded, na.rm = TRUE),
            min(percent_funded, na.rm = TRUE), 
            median(percent_funded, na.rm = TRUE), 
            max(percent_funded, na.rm = TRUE),
            mean(backers_count), 
            sd(backers_count),
            min(backers_count), 
            median(backers_count), 
            max(backers_count), 
            mean(avg_contribution, na.rm = TRUE), 
            sd(avg_contribution, na.rm = TRUE),
            min(avg_contribution, na.rm = TRUE), 
            median(avg_contribution, na.rm = TRUE), 
            max(avg_contribution, na.rm = TRUE)) %>%
  ungroup(state)

db_cleaned %>%
  filter(state == "failed" | state == "successful") %>%
  filter(percent_funded <= 400 & avg_contribution <= 250) %>%
  group_by(category_slug) %>%
  summarise(n(), 
            successe_rate = round(length(which(state == "successful"))/n()*100, 2), 
            min(percent_funded, na.rm = TRUE), 
            median(percent_funded, na.rm = TRUE), 
            max(percent_funded, na.rm = TRUE),
            mean(percent_funded, na.rm = TRUE), 
            sd(percent_funded, na.rm = TRUE),
            mean(as.numeric(backers_count)), 
            sd(as.numeric(backers_count)),
            min(as.numeric(backers_count)), 
            median(as.numeric(backers_count)), 
            max(as.numeric(backers_count)), 
            mean(avg_contribution, na.rm = TRUE), 
            sd(avg_contribution, na.rm = TRUE),
            min(avg_contribution, na.rm = TRUE), 
            median(avg_contribution, na.rm = TRUE), 
            max(avg_contribution, na.rm = TRUE)) %>%
  ungroup(category_slug)

db_cleaned %>%
  filter(state == "failed" | state == "successful") %>%
  filter(percent_funded <= 400 & avg_contribution <= 250) %>%
  group_by(category_parent_id) %>%
  summarise(n(), 
            success_rate = round(length(which(state == "successful"))/n()*100, 2), 
            mean(as.numeric(goal), na.rm = TRUE), 
            min(percent_funded, na.rm = TRUE), 
            median(percent_funded, na.rm = TRUE), 
            max(percent_funded, na.rm = TRUE),
            mean(percent_funded, na.rm = TRUE), 
            sd(percent_funded, na.rm = TRUE),
            mean(as.numeric(backers_count)), 
            sd(as.numeric(backers_count)),
            min(as.numeric(backers_count)), 
            median(as.numeric(backers_count)), 
            max(as.numeric(backers_count)), 
            mean(avg_contribution, na.rm = TRUE), 
            sd(avg_contribution, na.rm = TRUE),
            min(avg_contribution, na.rm = TRUE), 
            median(avg_contribution, na.rm = TRUE), 
            max(avg_contribution, na.rm = TRUE)) %>%
  ungroup(category_parent_id)
```

## Tidy text for words in project blurbs
```{r}
db_cleaned_tidy <- select(db_cleaned,
                          id, name, creator_id, location_short_name, 
                          category_slug, category_parent_id, 
                          created_at, launched_at, deadline, hype_length, campaign_length, 
                          spotlight, staff_pick, 
                          state, backers_count, pledged, goal, 
                          avg_contribution, percent_funded, 
                          blurb) %>% 
  unnest_tokens(word, blurb) %>% 
  anti_join(stop_words)
View(db_cleaned_tidy)

db_cleaned_tidy %>% 
  count(word, sort = TRUE) %>% 
  filter(word != "39") %>% 
  filter(word != "amp") %>% 
  filter(n >= 200) %>% 
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

## Predictive Analysis
```{r}
m <- lm (avg_contribution ~ percent_funded, data = db_cleaned)
summary(m)
```