---
title: "About The Data"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(knitr)
library(kableExtra)
```

#Data Dictionary

```{r echo=FALSE}
#Create data frame
dictionary <- as.data.frame(matrix(0, nrow = 29, ncol = 4, 
                                   dimnames = list(NULL, c("Name", "Description", "Type", "Values"))))

# Populate first column with variable names from df_engr
dictionary$Name <- c(colnames(df_engr))

# Manually write definitions
dictionary$Description <- c("Amount pledged compared to goal by deadline",
                            "Number of comments users post during campaign",
                            "Goal set at beginning of campaign, in local currency",
                            "Number of times page was updated during campaign",
                            "Number of backers that contributed to the project",
                            "Text description of the project",
                            "Days between launch and deadline",
                            "Mean amount pledged per backer, in local currency",
                            "Percent of goal received (%)",
                            "If successful, indicates if project is featured",
                            "Staff selected to receive 'Projects We Love' badge",
                            "Indicates location in the US or in another country",
                            "Indicates if creator provided any links to social media",
                            "Indicates if creator linked to Facebook",
                            "Indicates if creator linked to Twitter",
                            "Indicates if creator linked to YouTube",
                            "Number of social media links provided by creator",
                            "Indicates if the project page had a photo",
                            "Indicates if the project page had a video",
                            "Number of characters in reward structure description",
                            "Number of characters in full project description",
                            "Date of project launch (yyyy-mm-dd)",
                            "Month and year of project launch (mm-yyyy)",
                            "Year of project launch (yyyy)",
                            "Month of project launch (mm)",
                            "Ventile assigned to goal",
                            "Decile assigned to full description length",
                            "Decile assigned to reward description length",
                            "One of 15 buckets categorizing project field")

# Populate third column the variable type
dictionary$Type <- c(sapply(df_engr, class))
# Fix some variable types
dictionary[1,3] <- "factor"
dictionary[7,3] <- "numeric"
dictionary[10,3] <- "factor"
dictionary[11,3] <- "factor"
dictionary[12,3] <- "factor"
dictionary[13,3] <- "factor"
dictionary[14,3] <- "factor"
dictionary[15,3] <- "factor"
dictionary[16,3] <- "factor"
dictionary[17,3] <- "integer"
dictionary[18,3] <- "factor"
dictionary[19,3] <- "factor"
dictionary[23,3] <- "Date"
dictionary[24,3] <- "Date"
dictionary[25,3] <- "Date"
  
# Manually input values in fourth column
dictionary$Values <- list("0: failed; 1: successful",
                          paste(min(df_engr$comments_count), "-", max(df_engr$comments_count)),
                          paste(min(df_engr$goal), "-", max(df_engr$goal)),
                          paste(min(df_engr$updates_count), "-", max(df_engr$updates_count)),
                          paste(min(df_engr$backers_count), "-", max(df_engr$backers_count)),
                          "N/A",
                          paste(min(as.numeric(df_engr$campaign_duration)), "-", 
                                as.numeric(max(df_engr$campaign_duration))),
                          paste(min(df_engr$avg_contribution, na.rm = TRUE), "-",
                                max(df_engr$avg_contribution, na.rm = TRUE)),
                          paste(min(df_engr$percent_funded), "-", max(df_engr$percent_funded)),
                          "0: no spotlight; 1: spotlight",
                          "0: no badge; 1: 'Projects We Love' badge",
                          "0: other countries; 1: USA",
                          "0: no links to social media; 1: one or more links",
                          "0: no Facebook link; 1: Facebook link provided",
                          "0: no Twitter link; 1: Twitter link provided",
                          "0: no YouTube link; 1: YouTube link provided",
                          levels(df_engr$social_media_count),
                          "0: no photo; 1: has photo",
                          "0: no video; 1: has video",
                          paste(min(df_engr$reward_length), "-", max(df_engr$reward_length)),
                          paste(min(df_engr$description_length), "-", max(df_engr$description_length)),
                          paste(min(df_engr$date_launched), "to", max(df_engr$date_launched)),
                          paste(min(df_engr$mo_yr_launched), "to", max(df_engr$mo_yr_launched)),
                          paste(min(df_engr$yr_launched), "-", max(df_engr$yr_launched)),
                          paste(min(df_engr$mo_launched), "-", max(df_engr$mo_launched)),
                          levels(df_engr$goal_20),
                          levels(df_engr$description_length_10),
                          levels(df_engr$reward_length_10),
                          "art, comics, dance, design, fashion, food, film&video, games, journalism, music,
                          photography, technology, theater, publishing, crafts")

dictionary %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(2, width = "50em") %>%
  column_spec(4, width = "40em")
```

```{r include=FALSE}
rm(dictionary)
```

```{r include=FALSE, eval=FALSE}
#Data Cleaning
#Understand available explanatory variables and make the data friendly for analysis.
##db dimensions and column names

#120 columns, 50,596 rows
ncol(db)
nrow(db)
names(db)
```

```{r  include=FALSE, eval=FALSE}
##Check variables with only one level
#Six variables with only one level; we will remove these in db_cleaned.

for (j in 1:ncol(db)) {
  if (length(unique(db[[j]])) == 1) {
    print(colnames(db)[j])
  }
}
```

##Acknowledgements
The following resources were invaluable to the completion of the project:

* Text Mining with R: A Tidy Approach (Silge & Robinson, 2018; https://www.tidytextmining.com)
* stm: R Package for Structural Topic Models (Roberts, Stewart, & Tingley; https://cran.r-project.org/web/packages/stm/vignettes/stmVignette.pdf)
* Binary text classification with Tidytext and caret (Hvitfeldt, 2018; https://www.hvitfeldt.me/2018/03/binary-text-classification-with-tidytext-and-caret/)
* naivebayes package documentation (ftp://cran.r-project.org/pub/R/web/packages/naivebayes/naivebayes.pdf)
* Create Awesome HTML Table with knitr::kable and kableExtra (Zhu, 2018; https://haozhu233.github.io/kableExtra/awesome_table_in_html.html)
