---
title: "Data_Cleaning"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Data Collection and Cleaning

Raw data were obtained from Kickstarter using a custom python web scraping function. These data included 50,596 projects and 120 variables pertaining to the projects and their creators from the launch of Kickstarter in 2009 through December 2013. 

Of these projects, possible outcome states included failed, succesful, suspended, canceled, and purged. We excluded 1,246 projects with suspended, canceled, or purged outcome states. We excluded four additional projects whose funding state is inaccurate in terms of the amount pledged (e.g., state is listed as failed when the amout pledged exceeded the goal). The final dataset for analysis contained 49,350 projects.

Of the original 120 variables, 41 contained meaningful information for analyses. Selecting from, transforming, and performing additional computations resulted in 29 variables used in subsequent exploratory analysis and machine learning. These variables are described in the Data Dictionary below.

```{r include=FALSE}
library(DBI)
library(RSQLite)
library(MASS)
library(tidytext)
library(anytime)
library(ggplot2)
library(ggthemes)
library(scales)
library(car)
library(lubridate)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(stm)
library(quanteda)
library(dplyr)
library(rpart)
library(rpart.plot)
library(randomForest)
library(tidyverse)
library(glmnet)
```


```{r include=FALSE}
# Reads SQL database with two tables into R. Each SQL table becomes an R data frame, and they are merged as db.
mydb <- dbConnect(SQLite(), dbname = "../../Data/mlks_parsed.db")
db <- dbGetQuery(conn = mydb, 'SELECT * FROM Projects')
creators <- dbGetQuery(conn = mydb, 'SELECT * FROM Creators')
dbDisconnect(mydb)
db <- left_join(db, creators, by = "creator_id")
rm(creators)
rm(mydb)
```


```{r include=FALSE}
# Remove meaningless character strings
db$project_id[] <- lapply(db$project_id, gsub, pattern = 'kkst', replacement = '')
db[] <- lapply(db, gsub, pattern = '&#39;', replacement = '')
db[] <- lapply(db, gsub, pattern = ' &amp; ', replacement = '&')
db$category_slug[] <- lapply(db$category_slug, gsub, pattern = ' ', replacement = '_')
```


```{r include=FALSE}
#SQL database imported all variables as character type; change non-character variables.

db$project_id <- as.integer(db$project_id)
db$backers_count <- as.integer(db$backers_count)
db$canceled_at <- anytime(as.numeric(db$canceled_at))
db$category_color <- as.integer(db$category_color)
db$category_id <- as.integer(db$category_id)
db$category_parent_id <- as.character(db$category_parent_id)
db$category_position <- as.integer(db$category_position)
db$category_slug <- unlist(db$category_slug)
db$comments_count <- as.integer(db$comments_count)
db$converted_pledged_amount <- round(as.numeric(db$converted_pledged_amount), 2)
db$created_at <- anytime(as.numeric(db$created_at))
db$creator_id <- as.integer(db$creator_id)
db$deadline <- anytime(as.numeric(db$deadline))
db$failed_at <- anytime(as.numeric(db$failed_at))
db$full_description[is.na(db$full_description)] <- ""
db$fx_rate <- round(as.numeric(db$fx_rate), 2)
db$goal <- round(as.numeric(db$goal), 2)
db$id <- as.integer(db$id)
db$launched_at <- anytime(as.numeric(db$launched_at))
db$location_id <- as.integer(db$location_id)
db$pledged <- round(as.numeric(db$pledged), 2)
db$potd_at <- anytime(as.numeric(db$potd_at))
db$profile_background_image_attributes_id <- as.integer(db$profile_background_image_attributes_id)
db$profile_background_image_opacity <- round(as.numeric(db$profile_background_image_opacity), 1)
db$profile_feature_image_attributes_id <- as.integer(db$profile_feature_image_attributes_id)
db$profile_id <- as.integer(db$profile_id)
db$profile_blurb <- unlist(db$profile_blurb)
db$profile_link_text_color <- as.integer(db$profile_link_text_color)
db$profile_project_id <- as.integer(db$profile_project_id)
db$profile_state_changed_at <- anytime(as.numeric(db$profile_state_changed_at))
db$state_changed_at <- anytime(as.numeric(db$state_changed_at))
db$static_usd_rate <- round(as.numeric(db$static_usd_rate), 2)
db$successful_at <- anytime(as.numeric(db$successful_at))
db$suspended_at <- anytime(as.numeric(db$suspended_at))
db$updated_at <- anytime(as.numeric(db$updated_at))
db$updates_count <- as.integer(db$updates_count)
db$usd_pledged <- round(as.numeric(db$usd_pledged), 2)
db$video_height <- as.integer(db$video_height)
db$video_id <- as.integer(db$video_id)
db$video_width <- as.integer(db$video_width)
```


```{r include=FALSE}
#Make db_cleaned
#Remove unecessary variables.

db_cleaned <- dplyr::select(db, 
                     -category_id, -category_color, -category_position, -category_name, 
                     -category_urls_web_discover, 
                     -creator_avatar_medium, -creator_avatar_small, -creator_avatar_thumb, 
                     -creator_chosen_currency, 
                     -creator_id, -creator_slug, 
                     -creator_is_registered, 
                     -creator_urls_api_user, -creator_urls_web_user, 
                     -currency_symbol, -currency_trailing_code, -current_currency, 
                     -disable_communication, 
                     -id, 
                     -is_starrable, 
                     -items, 
                     -livestreams, 
                     -location_country, -location_id, -location_is_root, 
                     -location_localized_name, -location_short_name, -location_slug,
                     -location_urls_api_nearby_projects, -location_urls_web_discover, -location_urls_web_location,
                     -photo_1024x576, -photo_1536x864, 
                     -photo_ed, -photo_full, -photo_little, -photo_med, -photo_small, -photo_thumb, 
                     -profile_background_color, -profile_background_image_attributes_id, 
                     -profile_background_image_attributes_image_urls_baseball_card, 
                     -profile_background_image_attributes_image_urls_default, -profile_background_image_opacity, 
                     -profile_feature_image_attributes_id,
                     -profile_feature_image_attributes_image_urls_baseball_card, 
                     -profile_feature_image_attributes_image_urls_default,
                     -profile_id, -profile_project_id, 
                     -profile_link_background_color, -profile_link_text, -profile_link_text_color, 
                     -profile_link_url, -profile_name, 
                     -profile_should_show_feature_image_section, -profile_show_feature_image, 
                     -profile_text_color, 
                     -slug, 
                     -suspended_at, -canceled_at, -potd_at, -profile_state_changed_at, 
                     -urls_api_comments, -urls_api_project, -urls_api_updates, 
                     -urls_web_project, -urls_web_project_short, -urls_web_rewards, -urls_web_updates, 
                     -usd_pledged, -usd_type, -video, 
                     -video_base, -video_frame, -video_height, -video_high, -video_hls, -video_id, -video_width)
rm(db)
```

```{r include=FALSE}
#Remove projects with result anamolies
#We consider only failed or successful project for binomial classification problem.
#We remove four projects in which the actual outcome is not accurately reflected by $state.

#Consider only failed or successful projects for binomial classification
state_list <- c("failed", "successful")
db_cleaned <- db_cleaned[db_cleaned$state %in% state_list,]
rm(state_list)

#Isolate relevant variables into df_success
df_success <- db_cleaned[, c("pledged", "state", "goal")]

#Add $goal_met
df_success$goal_met <- df_success$pledged >= df_success$goal

#Compare $state to $goal_met
df_success$successful <- df_success$state == "successful"
(mean(df_success$goal_met == df_success$successful))

#Explore the errors
df_errors <- df_success[df_success$goal_met != df_success$successful,]
df_errors

#Consider only correctly classified projects
errors_to_remove <- which(df_success$goal_met != df_success$successful)
db_cleaned <- db_cleaned[-errors_to_remove,]

#Clean Up
rm(df_success)
rm(df_errors)
rm(errors_to_remove)
```


```{r include=FALSE}
##Create df_engr
df_engr <- data.frame(funded = as.numeric(db_cleaned$state == "successful"))

#Direct Ports
df_engr$comments_count <- db_cleaned$comments_count
df_engr$goal <- db_cleaned$goal
df_engr$updates_count <- db_cleaned$updates_count
df_engr$backers_count <- db_cleaned$backers_count
df_engr$full_description <- db_cleaned$full_description

#Campaign Stats
df_engr$campaign_duration = as.numeric(round((db_cleaned$deadline - db_cleaned$launched_at), 2))
df_engr$avg_contribution = round((db_cleaned$pledged/db_cleaned$backers_count), 2)
df_engr$percent_funded = round((db_cleaned$pledged/db_cleaned$goal*100), 2)

df_engr$spotlight <- as.numeric(as.character(factor(db_cleaned$spotlight, labels = c(0, 1))))
df_engr$staff_pick <- as.numeric(as.character(factor(db_cleaned$staff_pick, labels = c(0, 1))))
df_engr$usa = as.numeric(db_cleaned$country == "US")



#Media
df_engr$social_media <- as.numeric(as.character(factor(
                       (!is.na(db_cleaned$facebook) & !is.na(db_cleaned$twitter) & !is.na(db_cleaned$youtube)), labels = c(0, 1))))
df_engr$facebook <- as.numeric(!is.na(db_cleaned$facebook)) 
df_engr$twitter <- as.numeric(!is.na(db_cleaned$twitter)) 
df_engr$youtube <- as.numeric(!is.na(db_cleaned$youtube))
df_engr$social_media_count <- df_engr$facebook + df_engr$twitter + df_engr$youtube
df_engr$social_media_count <- as.factor(df_engr$social_media_count)

df_engr$photo_key[!is.na(db_cleaned$photo_key)] <- 1
df_engr$photo_key[is.na(db_cleaned$photo_key)] <- 0

df_engr$video_status[!is.na(db_cleaned$video_status)] <- 1
df_engr$video_status[is.na(db_cleaned$video_status)] <- 0

#Text Analysis
df_engr$reward_length <- nchar(as.character(db_cleaned$rewards))
df_engr$description_length <- nchar(db_cleaned$full_description)

#Dates
df_engr$date_launched <- as.Date(db_cleaned$launched_at, format="%m/%d/%Y")
df_engr$mo_yr_launched <- format((df_engr$date_launched),"%m-%Y")
df_engr$yr_launched <- format((df_engr$date_launched),"%Y")
df_engr$mo_launched <- format((df_engr$date_launched),"%m")

#Quantiles
df_engr$goal_20 = cut(db_cleaned$goal, breaks = unique(quantile(db_cleaned$goal, seq(0, 1, by = .05))), include.lowest = TRUE)
df_engr$description_length_10 = cut(df_engr$description_length, breaks = unique(quantile(df_engr$description_length, seq(0, 1, by = .1))), include.lowest = TRUE)
df_engr$reward_length_10 <- cut(df_engr$reward_length, breaks = unique(quantile(df_engr$reward_length, seq(0, 1, by = .1))), include.lowest = TRUE)


#Categories
category_map = list(
  "1" = "art",
  "3" = "comics",
  "6" = "dance",
  "7" = "design",
  "9" = "fashion",
  "10" = "food",
  "11" = "film&video",
  "12" = "games",
  "13" = "journalism",
  "14" = "music",
  "15" = "photography",
  "16" = "technology",
  "17" = "theater",
  "18" = "publishing",
  "26" = "crafts")

category = c()
for (id in db_cleaned$category_parent_id) {
  category <- append(category, category_map[id])
}
df_engr$category <- as.character(category)
df_engr$category <- as.factor(df_engr$category)
rm(category)
rm(category_map)
rm(id)

```

```{r include=FALSE}
##Export csv
#write.csv(db_cleaned, file = "db_cleaned.csv")
```



