---
title: "Key Findings"
output: html_document
---

# Key Findings

## `percent_funded`
Non-normal distribution shows that most projects over ~75% of their goal wind up being successful. There may be outside manipulation happening due to Kickstarter promotions of projects that are near their goals, or personal donations by the creators and/or creators personal connections.

```{r echo=FALSE}

df_filtered_by_percent_funded <- df_engr %>%
  filter(!is.na(percent_funded) & percent_funded <= 400)

# Non-normal distribution
df_filtered_by_percent_funded %>% 
  ggplot(aes(x = percent_funded)) + 
  geom_histogram(fill = "#332288")

#Clean up
rm(df_filtered_by_percent_funded)
```


## `staff_pick`
This flag denotes projects that have received the "Projects We Love" badge and get prominently features on the website, newsletters, and blogs. Kickstarter staff clearly has a great eye for promising projects and/or some strong marketing impact.

'staff_pick` has exciting implications for the continuation of this project. As machine learning applications become more widely used and increase in efficacy, often the benchmark is, "Can it do better than a human?" `staff_pick` serves as a proxy for the best human judgment has to offer and therefore serves as a benchmark for our machine learning.

It is important to note that we do not anticipate being able to replicate this success rate as there is a boosting effect from the marketing efforts that should increase the success rate well beyond Day Zero probabilities.

[Kickstarter - Projects We Love](https://www.kickstarter.com/discover/recommended)

```{r echo=FALSE}
df_engr %>%
  group_by(staff_pick) %>%
    summarise(n(), mean(funded)) %>% 
  ungroup(staff_pick)
```